Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-23 Docs/TODAES/paper.tex
replace timeouts and memory-outs
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

\usepackage{minted}
\newcolumntype{C}[1]{>{\Centering}m{#1}}
\renewcommand\tabularxcolumn[1]{C{#1}}
\usepackage{tabularx,ragged2e,booktabs,caption}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
int i;
#pragma omp parallel for
for (i = 0; i < 10; i++)
  a[i] = 2 * i;
\end{minted}
\caption{OpenMP basic Example.}
\label{lst:example}
\end{listing}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A time out condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory out (MO) occurs when the tool reaches $15$GB of memory.

@@

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (time-outs) related to RC6, Fuzzy and Mars benchmarks.

@@

Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution. No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.

>>>>

\usepackage{minted}
\usemintedstyle{bw}

\newcolumntype{C}[1]{>{\Centering}m{#1}}
\renewcommand\tabularxcolumn[1]{C{#1}}
\usepackage{tabularx,ragged2e,booktabs,caption}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{matlab}
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{minted}
\caption{OpenMP basic Example.}
\label{lst:example}
\end{listing}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$GB of memory.

@@

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.

@@

Note that RC$6$ produced timeout for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution. No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.
